---
title: "Challenge-5"
author: "Misra Anandita"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Local Variable Shadowing 

Create an R function that defines a global variable called `x` with a value of 5. Inside the function, declare a local variable also named `x` with a value of 10. Print the value of `x` both inside and outside the function to demonstrate shadowing.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
x<- 5 
declare <- function(x){x<-10 
return(x)}

sprintf("The value of x outside the function is %d",x)

declare(x)
```
<br>

#### Question-2: Modify Global Variable

Create an R function that takes an argument and adds it to a global variable called `total`. Call the function multiple times with different arguments to accumulate the values in `total`.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
total<-1
add_total<- function(x){
  total <<- total + x
  print(total)
  }
add_total(1)
add_total(2)
add_total(4)
add_total(7)
```
<br>

#### Question-3: Global and Local Interaction 

Write an R program that includes a global variable `total` with an initial value of 100. Create a function that takes an argument, adds it to `total`, and returns the updated `total`. Demonstrate how this function interacts with the global variable.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
total<- 100
update_total<- function(x){total <<- total + x
return(total) }
update_total(50)
update_total(100)
```
<br>


#### Question-4: Nested Functions

Define a function `outer_function` that declares a local variable `x` with a value of 5. Inside `outer_function`, define another function `inner_function` that prints the value of `x`. Call both functions to show how the inner function accesses the variable from the outer function's scope.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
outer_function<- function(){x<-5 
inner_function<-function(){print(x)}
inner_function()
}
outer_function()


```
<br>

#### Question-5: Meme Generator Function

Create a function that takes a text input and generates a humorous meme with the text overlaid on an image of your choice. You can use the `magick` package for image manipulation. You can find more details about the commands offered by the package, with some examples of annotating images here: https://cran.r-project.org/web/packages/magick/vignettes/intro.html

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(magick)
meme<-image_read("meme.png") 
print(meme) 

```
<br>

#### Question-6: Text Analysis Game  

Develop a text analysis game in which the user inputs a sentence, and the R function provides statistics like the number of words, characters, and average word length. Reward the user with a "communication skill level" based on their input.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here

  
  play_game<- function(){
    #input_sentence<- readline("Enter sentence- ") 
    input_sentence <- "Hello from NM2207"
  number_of_characters<- nchar(input_sentence)
 words <- strsplit(input_sentence, "\\s+")[[1]]
  number_of_words<- length(words)
  skill <<- ""
  if (number_of_words<6) {
    skill <<- "Beginner"
}
  else if(number_of_words<9) {
    skill <<- "Intermediate"
}
  else {
    skill <<- "Expert"

  }
    
  average_word_length <- number_of_characters/number_of_words
  print(number_of_characters)
  print(number_of_words)
  print(average_word_length)
  print(skill)

  
  }


  play_game()
  
   
  
```
<br>