---
title: "Challenge-4"
author: "Misra Anandita"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style>
p.comment {
background-color: #DBDBDB;
padding: 10px;
border: 1px solid black;
margin-left: 25px;
border-radius: 5px;
font-style: italic;
}

</style>

## Questions
<br>

Load the "CommQuest2023.csv" dataset using the `read_csv()` command and assign it to a variable named "comm_data." 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(tidyverse)
comm_data <- read_csv("CommQuest2023_Larger.csv")
```
<br>


#### Question-1: Communication Chronicles

Using the select command, create a new dataframe containing only the "date," "channel," and "message" columns from the "comm_data" dataset.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
select(comm_data,date,channel,message)
```
<br>

#### Question-2: Channel Selection

Use the filter command to create a new dataframe that includes messages sent through the "Twitter" channel on August 2nd.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data %>% filter(channel == "Twitter", date == "2023-08-02")
```
<br>

#### Question-3: Chronological Order

Utilizing the arrange command, arrange the "comm_data" dataframe in ascending order based on the "date" column.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
arrange(comm_data,date)
```
<br>

#### Question-4: Distinct Discovery

Apply the distinct command to find the unique senders in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data %>% distinct(sender)
```
<br>

#### Question-5: Sender Stats

Employ the count and group_by commands to generate a summary table that shows the count of messages sent by each sender in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here

comm_data %>% group_by(sender) %>% summarise(count = n())
```
<br>

#### Question-6: Channel Chatter Insights

Using the group_by and count commands, create a summary table that displays the count of messages sent through each communication channel in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data %>% group_by(channel) %>% summarise(count = n())

```
<br>

#### Question-7: Positive Pioneers

Utilize the filter, select, and arrange commands to identify the top three senders with the highest average positive sentiment scores. Display their usernames and corresponding sentiment averages.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data %>% group_by(sender) %>% summarise(mean_sentiment = mean(sentiment)) %>% arrange(desc(mean_sentiment)) %>% ungroup() %>% select(sender, mean_sentiment) %>% slice(1:3)
```
<br>

#### Question-8: Message Mood Over Time

With the group_by, summarise, and arrange commands, calculate the average sentiment score for each day in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data %>% group_by(date) %>% summarise(mean_sentiment = mean(sentiment)) %>% arrange(date)
```
<br>

#### Question-9: Selective Sentiments

Use the filter and select commands to extract messages with a negative sentiment score (less than 0) and create a new dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data %>% filter(sentiment<0)%>% select(message, sentiment)
```
<br>

#### Question-10: Enhancing Engagement

Apply the mutate command to add a new column to the "comm_data" dataframe, representing a sentiment label: "Positive," "Neutral," or "Negative," based on the sentiment score.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data%>% mutate(sentiment_label = case_when(sentiment>0~"Positive", sentiment<0~"Negative", sentiment == 0~"Neutral"))
```
<br>

#### Question-11: Message Impact

Create a new dataframe using the mutate and arrange commands that calculates the product of the sentiment score and the length of each message. Arrange the results in descending order.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data%>% mutate (product_sentiment_length = sentiment * nchar(message)) %>% arrange(desc(product_sentiment_length))
```
<br>

#### Question-12: Daily Message Challenge

Use the group_by, summarise, and arrange commands to find the day with the highest total number of characters sent across all messages in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data%>% group_by(date)%>% summarise(total_characters = sum(nchar(message)))%>% arrange(desc(total_characters))%>% slice(1)
```
<br>

#### Question-13: Untidy data

Can you list at least two reasons why the dataset illustrated in slide 10 is non-tidy? How can it be made Tidy?

**Solution:** Under subject column, there is a row interspaced in between, of EMPLOYMENT STATUS with no observation associated with it. To make it tidy, "Employment Status" could have been added in the name of the column itself. There are multiple columns under the single column of "United States". This makes data untidy and confusing to understand and use because of the existence of these sub-columns. We can make it tidy by removing the column of "United States" and keeping the multiple columns under it. The fact that the data is of United States can simply be mentioned in another place like the "Subject-Employment Status of United States". The data set will be tidy since it will have the separate columns of estimate, margin of error, percent, percent margin of error next to the column of subject-employment status of United States as mentioned previously. There are multiple observations within observations i.e.  multiple categories within categories eg- the category of population 16 years and over has "in labor force" which has civilian labor force, employed, unemployed, etc. It can be made tidy by keeping such categories in the column but making clear the names of the observations so that each observation is specified to be under a specific category without confusion- eg- since there are 3 observations named civilian labour force under three different observations in an effort to categorise but the names of these observations can be changed to specify say- civilian labor force in the labor force of females 16 years and over. these observations can be named more clearly to include their category in the name to avoid confusion as to which category they belong to. We are keeping the observations under the same column since all categories and sub-categories have values in the other columns and therefore, all observations are equally important- it is safe to keep them under one column of Subject and specifying their names clearly so that the same words are not used for different observations of different catgeories like the confusion in repetition of the observation- "civilian labor force". 