---
title: "Challenge-6"
author: "Misra Anandita"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Countdown Blastoff (While Loop)

Create a program that simulates a rocket launch countdown using a while loop. Start from 10 and countdown to "Blastoff!" with a one-second delay between each countdown number. Print a message when the rocket launches.

**Hint:** You may want to use `cat` command to print the countdown and `Sys.sleep` for incorporating the delay

**Output preview:** Here is how the countdown could look like 

```{r, out.height= "20px",out.width= "200px",echo=TRUE}

```

```{r, out.height= "20px",out.width= "200px",echo=FALSE}


```

**Solutions:**

```{r, eval=T,echo=TRUE}
# Enter code here
Countdown<- function(countdown_number){
  if(countdown_number>0){
    cat(countdown_number, "seconds left...") 
    Sys.sleep(1)
  } else{
    cat("Blastoff!\n")
  }
}

countdown_time<- 10

while(countdown_time>=0){
  Countdown(countdown_time)
  countdown_time <- countdown_time - 1
}

cat("The rocket has launched!\n")

```
<br>

#### Question-2: Word Reverser (for Loop)

Develop a program that takes a user-entered word and uses a while loop to print the word's characters in reverse order. For example, if the user enters "hello," the program should print "olleh."

**Hint:** You may want to use `substr` command to access each character of the input word, and `paste` command to join the reversed letters one at a time

**Solutions:** 

```{r, eval=T,echo=TRUE}
# Enter code here
reverse_the_word<- function(word_input){
  reversed_word <- ""
  i<- nchar(word_input)
  while (i>0) {
    reversed_word<- paste(reversed_word, substr(word_input, i,i))
    i<- i-1
  }
  return(reversed_word)
}
 
user_input_word<- readline(prompt = "Enter your word- ")

Word_Reversed<-reverse_the_word(user_input_word)

cat("This is your word in reverse:", Word_Reversed, "\n")
```
<br>
